Demand Forecasting of individual Probability Density Functions with Machine Learning

### 2020-07-21 LaTex/paper.tex
minor rewording

\begin{abstract}
Demand forecasting is a central component for many aspects of supply chain operations, as it provides crucial input for subsequent decision making like ordering processes. While machine learning methods can significantly improve prediction accuracy over traditional time series forecasting, the calculated predictions are often mere point estimations for the conditional mean of the underlying random distribution, and the most powerful approaches, like deep learning, are usually opaque in terms of how its individual predictions can be interpreted. We present an extension to our earlier work on a supervised machine learning method called Cyclic Boosting to predict full individual probability density functions in form of negative binomial distributions, that are fully explainable on the individual prediction level. Also, we describe new techniques for both qualitative and quantitative evaluation of predicted probability density functions by comparison with observed data.
\end{abstract}

@@

\subsection{Cyclic Boosting Recap}
\label{sec:CB}

In our earlier work \cite{Wick2019}, we have presented a new machine learning algorithm, Cyclic Boosting, which can be categorized as a generalized additive model with a cyclic coordinate descent optimization featuring a boosting-like update of parameters. The major benefits of Cyclic Boosting are that it is not only extremely performant in practical applications, like demand forecasting, at large scale, but also fully explainable. Traditional machine learning algorithms are typically "black box'' approaches, where the individual decision cannot be explained. Cyclic Boosting on the other hand allows to follow how each individual prediction was made. The main idea of this algorithm is the following: When used for regression, denoted as multiplicative regression mode, the predictions $\hat{y_i}$ of the  target variable $Y \in [0,\infty)$ can be calculated in the following way:

>>>>

\begin{abstract}
Demand forecasting is a central component for many aspects of supply chain operations, as it provides crucial input for subsequent decision making like ordering processes. While machine learning methods can significantly improve prediction accuracy over traditional time series forecasting, the calculated predictions are often mere point estimations for the conditional mean of the underlying random distribution, and the most powerful approaches, like deep learning, are usually opaque in terms of how its individual predictions can be interpreted. Using the novel supervised machine learning method ``Cyclic Boosting'', complete individual probability density functions in form of negative binomial distributions can be predicted instead of simple point estimates. Additionally, each single prediction is explainable which is a major benefit in practice as individual forecasts can be understood by the practitioner and ``black-box'' models can be avoided. Also, we describe new techniques for both qualitative and quantitative evaluation of predicted probability density functions by comparison with observed data.
\end{abstract}

@@

\subsection{Cyclic Boosting Algorithm}
\label{sec:CB}

Cyclic Boosting \cite{Wick2019} is a novel machine learning algorithm that can be categorized as a generalized additive model with a cyclic coordinate descent optimization featuring a boosting-like update of parameters. The major benefits of Cyclic Boosting are that it is not only extremely performant in practical applications, like demand forecasting, at large scale, but also fully explainable. Traditional machine learning algorithms are typically "black box'' approaches, where the individual decision cannot be explained. Cyclic Boosting on the other hand allows to follow how each individual prediction was made. The main idea of this algorithm is the following: When used for regression, denoted as multiplicative regression mode, the predictions $\hat{y_i}$ of the  target variable $Y \in [0,\infty)$ can be calculated in the following way:
